How to fix IR

### 2017-09-11 paper/netsMatter.tex
email fix
sim analysis done
more mods

 \author[Tellez]{Juan Tellez}
 \address{Juan Tellez}
 \curraddr{Department of Political Science, Duke University}
 \email{juan.f.tellez@duke.edu}

@@

@@

\begin{table}
\caption{Features of the Studies Replicated. }
\scalebox{.8}{
	\begin{tabular}{ccrcc}
		Study & Model & N. of Dyads & Type of Dyads & Clustered $\sigma_{\hat{\beta}}$ \\ \toprule
		Weeks (2012) & Logit & $901,540$ & Directed & Robust \\
		Reiter \& Stam (2003) & Logit & $753,456$ & Directed & Robust \\
		Rose (2004) &OLS&$234,597$&Directed&Robust \\
		McDonald (2004) & Logit &$92,354$& Undirected &Robust\\
		Gibler (2017) &Logit& $650,557$&UnDirected& no \\
	\bottomrule
	\end{tabular}
}
\end{table}

@@

\begin{table}[ht]
\centering
	\begin{tabular}{l| p{7cm} l}
	& \multirow{2}{*}{Central Finding} & Does it Replicate \\ 
	& &  in a Network Model? \\
	\hline\hline
		Weeks (2012) & Bosses, Juntas and Strongmen are more Aggressive, Machines are Not & \textbf{Fails to Replicate} \\
		\hline
		Reiter \& Stam (2003) & Personalist Regimes Attack Democracies, Not Vice Versa & Replicates \\ 
		\hline
		Rose (2004) & WTO Membership Does not Effect Trade & Replicates \\ 
		\hline
		McDonald (2004) & Lower Trade Barriers and Higher Trade Lead to Peace & \textbf{Fails to Replicate} \\ 
		\hline
		Gibler (2017) & Power Parity at time of Entry to International System Inceases Conflict & \textbf{Fails to Replicate} \\ 
	\hline\hline
	\end{tabular}
	\caption{Here we provide a brief summary of the key variable in each of the five replications and a note about whether or not the finding is replicated when using our network based approach. Cases in which the finding is not replicated are highlighted in bold.}
	\label{tab:modelFindingSumm}
\end{table}

>>>>

 \author[Tellez]{Juan Tellez}
 \address{Juan Tellez}
 \curraddr{Department of Political Science, Duke University}
 \email{juan.tellez@duke.edu}

@@

\begin{figure}
	\centering
	\caption{Coverage in parameter when homophily is ignored.}
	\label{fig:ameCalib}
	\includegraphics[width=1\textwidth]{ameSimCover_mu.pdf} \\
	\includegraphics[width=1\textwidth]{ameSimCover_beta.pdf}
\end{figure}

\begin{figure}
	\centering
	\caption{Correlation between missing variable and multiplicative random effect in AME.}
	\label{fig:ameCorr}
	\includegraphics[width=1\textwidth]{ameSimCorr.pdf} \\
\end{figure}

@@

\begin{table}
\caption{Features of the Studies Replicated. }
	\begin{tabular}{lcccccc}
		 & Model & \# of Actors & Years  & \# of Dyads & Type of Dyads & Clustered $\sigma_{\hat{\beta}}$ \\ \hline\hline
		Weeks (2012) & Logit & & & $901,540$ & Directed & Robust \\
		Reiter \& Stam (2003) & Logit & & & $753,456$ & Directed & Robust \\
		McDonald (2004) & Logit & & & $92,354$ & Undirected & Robust\\		
		Gibler (2017) & Logit & & & $650,557$ & UnDirected & no \\		
		Rose (2004) & OLS & & & $234,597$ & Directed & Robust \\
	\hline\hline
	\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
	\begin{tabular}{l| p{7cm} l}
	& \multirow{2}{*}{Central Finding} & Does it Replicate \\ 
	& &  in a Network Model? \\
	\hline\hline
		Weeks (2012) & Bosses, Juntas and Strongmen are more Aggressive, Machines are Not & \textbf{Fails to Replicate} \\
		\hline
		Reiter \& Stam (2003) & Personalist Regimes Attack Democracies, Not Vice Versa & Replicates \\ 
		\hline
		McDonald (2004) & Lower Trade Barriers and Higher Trade Lead to Peace & \textbf{Fails to Replicate} \\ 
		\hline
		Gibler (2017) & Power Parity at time of Entry to International System Inceases Conflict & \textbf{Fails to Replicate} \\ 		
		\hline
		Rose (2004) & WTO Membership Does not Effect Trade & Replicates \\ 
	\hline\hline
	\end{tabular}
	\caption{Here we provide a brief summary of the key variable in each of the five replications and a note about whether or not the finding is replicated when using our network based approach. Cases in which the finding is not replicated are highlighted in bold.}
	\label{tab:modelFindingSumm}
\end{table}
